---
title: "ExerciseAndNote"
output: md_document
---

Example **Solution** 
Note :
Dc: Did not Have A diseases
D : Have A disease
+ : Positive Have A disease
- : Negative Have a disease

Sensitifity : P(+|D)
Specificity : P(-|Dc)

P(D) : 0.01
P(Dc) : 1 - 0.01 =0.99

P(+|D) = 0.997
P(-|D) = 0.003

P(-|Dc) = 0.985
P(+|Dc) = 0.015

```{r}
# Ans = P(D|+)

ans = 0.997 * 0.01 / ((0.997*0.01) + (0.99 * 0.015))
cat("So the probability a person Have Disease given positive is : " ,ans , "\n")

# ComplemenAns
# Ansc = P(Dc|+)
ANSc <- 1 - ans
cat("So the probability a person didnt have a disease given positive is" , ANSc)

```


Diagnostic Likelihood ratios :
Summarize The Evidence we have 

P(D|+)    P(+|D) * P(D)
------- = ----------------
P(Dc|+)   P(+|Dc) * P(Dc)

Found it hard to grasp , :V



1. I pull a card from a deck and do not show you the result. I say that the resulting card is a heart. What is the probability that it is the queen of hearts?

**ANSWER** :
P(QHeart | P(HEART)) = P(QHeart$HEART) / P(HEART) 
```{r}
Heart <- 13/52
# Because QHeart is subset of heart then we can write
# P(QHEART$HEART) = P(Qheart)
QHeart <- 1/52
QHeart <- cat("Probability the card is queen of heart is : " ,QHeart / Heart)


```

2. The odds associated with a probability, p, are defined as?
**Answer**:
DLRs

3. The probability of getting two sixes when rolling a pair of dice is? 
**ANSWER**
We have 2 Dice , 6 * 6 = 36 , so there are 36 possibilities . i.e {1,2}{2,1}{6,6}

```{r}
# We hvae 2 Dice 
cat( 1 / 36)


```

4. The probability that a manuscript gets accepted to a journal is 12% (say). However, given that a revision is asked for, the probability that it gets accepted is 90%. Is it possible that the probability that a manuscript has a revision asked for is 20%?

**Answer** 
P(ACC) = 0.12
P(ACC^) = 0.88

P(ACC|revision) = 0.90
P(ACC^| revision) = 0.10

P(Revision) = 0.2

ASked :
P(ACC$revision) = P(Revision) * P(ACC|revision) = 0.2 * 0.90

```{r}

Ans = 0.20 * 0.90
cat("So the probability person get the manuscript and has a revision is : " , Ans , "Which is impossible Because P(ACC) is : " , 0.12)

```

5. Suppose 5% of housing projects have issues with asbestos. The sensitivity of a test for asbestos
is 93% and the specificity is 88%. What is the probability that a housing project has no asbestos given a negative test expressed as a percentage to the nearest percentage point? 

**ANSWER**
P(asbestos) = 0.05
P(asbestos^) = 0.95

p(+|asbestos) = 0.93 <- Sensitivity
p(-|asbestos) = 0.07

p(-|asbestos^) = 0.88 <- Specifity
p(+|asbestos^) = 0.12

ASked :
P(asbestos^|negative) =                 p(negative|asbestos^)p(asbestos^)
                        ------------------------------------------------------------------
                        p(negative|asbestos^)p(asbestos^) + P(Negative|asbestos)p(asbestos) 
                        
```{r}

ans = 0.88 * 0.95 / ((0.88*095 + 0.07 * 0.05 ) ) 
cat("So The probability has no asbestos given negative is " , ans * 100)
```