---
title: "PDFStats"
output: md_document
---

```{r}
x <- c(-0.5,0,1,1,1.5)
y <- c(0,0,2,0,0)
plot(x , y, lwd = 3 ,frame = F ,type = "l")

```


## Recall That A Distribution must be valid
### 1. Non negative (A.K.A Above the horizontal axis everywhere)
### 2. Easy to get the are , i dont know what this mean ,i guess this mean easy to get the intervals 
```{r}

# question Of Interest 
# Now consider answering the following question. 
# What is the probability that 75% or fewer ofcalls
# get addressed?
# Remember Triangle formula ?
# 1/2 * height * length
print( (1.5 * 0.75)/ 2)
?pbeta()

```

```{r}

# # If you want to use this function find the mode of  your distribution 
# 
# Mode <- function(x) {
#   GetUnique <- unique(x)
#   GetUnique[which.max(tabulate(match(x , x)))]
# }
# xvarmode = Mode(x = x)
# print(xvarmode)
# yvarmode = Mode(x = y)

print(stats::pbeta(q = 0.75 , shape1 = 2 , shape2 = 1))

```


Exercises Solution :

1. Can you add the probabilities of any two events to get the probability of at least one occurring?
**Answer** : Nope , you need to substract it with the intersection, but if you want to add , follow this thumb rule : P(AUB) = P(A) + P(B) - P(A$B)

2. I define a PMF, p so that for x = 0 and x = 1 we have p(0) = -0:1 and p(1) = 1.1. Is this a valid PMF? 
**Answer** :No ! Remember it's probability value betweeen 0 - 1 

3. What is the probability that 75% or fewer calls get answered in a randomly sampled day from the population distribution from this chapter?

**Answer** :
```{r}
cat("So the Probability of 75% or fewer calls get answered is :",stats::pbeta(0.75 , shape1 = 2 , shape2 = 1))
```

4. The 97.5th percentile of a distribution is?
**Answer** : 
```{r}
cat("So the Probability of 97.5% or fewer calls get answered is :" ,stats::qbeta(0.975 ,shape1 = 2, shape2= 1))

```

5. Consider influenza epidemics for two parent heterosexual families. Suppose that the probability is 15% that at least one of the parents has contracted the disease. The probability that the father has contracted influenza is 10% while that the mother contracted the disease is 9%. Whatis the probability that both contracted influenza expressed as a whole number percentage?
**Answer** : 
Suppose that disease is influenza
A : father
B : Mother
P(AUB) :15%  Mother or Father have the disease <"At least" is the key>
P(A) : 10% or P(Ac) = 90%
P(B) : 9% or p(Bc) = 91%
P(A$B) : is going to be both mother and father have the disease
```{r}
cat("So there are : " ,0.10 + 0.09 - 0.15 ,"Chance both parent have the disease")

cat("And :" , 0.9 + 0.91 - 0.85 , "Chance both parent haven't the diseaese")

```

6. A random variable,X, is uniform, a box from 0 to 1 of height 1. (So that it’s density is f(x) = 1
for 0 <= x <= 1.) What is it’s median expressed to two decimal places? .
**Answer**
```{r}
x <- stats::runif(1000)
cat("The mEdian Is obvio " , stats::punif(0.5 , min = 0 ,max= 1))
```


7. If a continuous density that never touches the horizontal axis is symmetric about zero, can we say that its associated median is zero? yeah,

